\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-09-28 draft.tex
correct \tau^ad to not be bolded vector

\newcommand{\ve}{\theta}
\newcommand{\ta}{\theta}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\al}{\alpha}
\newcommand{\Ta}{\Theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\btad}{\bm{\tau^{ad}}}
\newcommand{\bte}{\bm{\tau^E}}
\newcommand{\btn}{\bm{\tau^n}}
\newcommand{\ga}{\gamma}

@@

Figure~\ref{fig:ext} illustrates the timing of the game. Taking the trade-agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} and levels of antidumping duties $\btad = \left(\tau^{ad},\tau^{*ad}\right)$ as given, the import-competing firms jointly attempt to persuade the government agency to renew the antidumping duties by choice of lobbying effort $e$.

@@

The government agency will renew the antidumping duty if the median actor's utility from the antidumping duty is higher than his utility from the trade agreement tariffs, i.e. if
\begin{equation}
  W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right)
  \label{eq:lwcg}
\end{equation}

The outcome of the decision on whether or not to renew the antidumping duties is not known to \textit{any} player until the uncertainty over the identity of the median governmental actor is resolved at the moment the decision is made. I represent the probability that antidumping duties are renewed as:
\begin{multline}
  r(e,\bta,\btad) = \expect_{\ga|e} \bm{1} [ W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) ] \\ = \Pr [ W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) | e]
  \label{eq:b}
\end{multline}

The lobby chooses its level of effort as a function of the trade agreement tariffs and the antidumping duties, given the implications of that choice on the government agency's probability of breaking the agreement. The lobby maximizes probability-weighted profits net of effort:
\[
  \max_{e} r(e,\bta,\btad) \pi(\tau^{ad}) + [1 - r(e,\bta,\btad)] \pi(\tau^a) - e
\]
The first order condition shows that the lobby balances the cost of an extra dollar of expenditure with the higher profits from a trade war weighted by the increase in the probability of provoking the trade war:
\begin{equation}
	\frac{\partial r(e,\bta,\btad)}{\partial e} \left[ \pi(\tau^{ad})  - \pi(\tau^a) \right] = 1 
	\label{eq:lobbyfoc}
\end{equation}
Assumption [old assumption3] and Result~\ref{res:bincC} ensure the second order condition. To guarantee an interior solution, we need
  \begin{equation}
	  \frac{\partial r(0,\bta)}{\partial e} \left[ \pi(\tau^{ad}) - \pi(\tau^a) \right] > 1.
		\label{ine:lobint}	
  \end{equation}
If the executives were to set $\tau^{ad} = \tau^a$, there would be no incentive for the lobby to make a positive contribution. There are some other cases in which it is in the executives' interest to set trade agreement tariffs so as to disengage the lobby. The following results only hold when the marginal impact of the first lobbying dollar on the break probability is sufficiently high to make engaging in the political process worthwhile for the lobby.

>>>>

\newcommand{\ve}{\theta}
\newcommand{\ta}{\theta}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\al}{\alpha}
\newcommand{\Ta}{\Theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\tad}{\tau^{ad}}
\newcommand{\bte}{\bm{\tau^E}}
\newcommand{\btn}{\bm{\tau^n}}
\newcommand{\ga}{\gamma}

@@

Figure~\ref{fig:ext} illustrates the timing of the game. Taking the trade-agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} and the antidumping duty level $\tad$ as given, the import-competing firms jointly attempt to persuade the government agency to renew the antidumping duties by choice of lobbying effort $e$.

@@

The government agency will renew the antidumping duty if the median actor's utility from the antidumping duty is higher than his utility from the trade agreement tariffs, i.e. if
\begin{equation}
  W_G(\tad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right)
  \label{eq:lwcg}
\end{equation}

The outcome of the decision on whether or not to renew the antidumping duties is not known to \textit{any} player until the uncertainty over the identity of the median governmental actor is resolved at the moment the decision is made. I represent the probability that antidumping duties are renewed as:
\begin{multline}
  r(e,\bta,\tad) = \expect_{\ga|e} \bm{1} [ W_G(\tad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) ] \\ = \Pr [ W_G(\tad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) | e]
  \label{eq:b}
\end{multline}

The lobby chooses its level of effort as a function of the trade agreement tariffs and the antidumping duties, given the implications of that choice on the government agency's probability of breaking the agreement. The lobby maximizes probability-weighted profits net of effort:
\[
  \max_{e} r(e,\bta,\tad) \pi(\tau^{ad}) + [1 - r(e,\bta,\tad)] \pi(\tau^a) - e
\]
The first order condition shows that the lobby balances the cost of an extra dollar of expenditure with the higher profits from a trade war weighted by the increase in the probability of provoking the trade war:
\begin{equation}
	\frac{\partial r(e,\bta,\tad)}{\partial e} \left[ \pi(\tau^{ad})  - \pi(\tau^a) \right] = 1 
	\label{eq:lobbyfoc}
\end{equation}
Assumption [old assumption3] and Result~\ref{res:bincC} ensure the second order condition. To guarantee an interior solution, we need
  \begin{equation}
	  \frac{\partial r(0,\bta)}{\partial e} \left[ \pi(\tau^{ad}) - \pi(\tau^a) \right] > 1.
		\label{ine:lobint}	
  \end{equation}
If the executives were to set $\tau^{ad} = \tau^a$, there would be no incentive for the lobby to make a positive contribution. There are some other cases in which it is in the executives' interest to set trade agreement tariffs so as to disengage the lobby. The following results only hold when the marginal impact of the first lobbying dollar on the break probability is sufficiently high to make engaging in the political process worthwhile for the lobby.
